Evaluating the Decency and Consistency of Data Validation Tests Generated by LLMs

### 2024-04-01 paper/paper.qmd
Fix quotes for consistency

Role is an aspect of a prompt that is provided to the LLM before the main prompt content. We considered two different roles, one that positioned the LLM as a helpful assistant, and the other that positioned the LLM as an experienced data scientist (@fig-role). We were expecting that the expert role would result in better code, but there was no obvious difference in terms of decency (@fig-role-1) or consistency (@fig-role-2). Although it is notable that there are no responses rated 1/5 with the "Expert" role. Their mean decency did not differ by much in either case with 3.12 and 3.32 for 'Helpful' and 'Expert', respectively, while mean consistency was 3.35 and 3.19.

@@

The responses that 'excelled' in their decency scores tended to bring a new tool beyond what was in the gold standard code suite -- for instance, generating a class with functions, or saving the results as a JSON.

>>>>

Role is an aspect of a prompt that is provided to the LLM before the main prompt content. We considered two different roles, one that positioned the LLM as a helpful assistant, and the other that positioned the LLM as an experienced data scientist (@fig-role). We were expecting that the expert role would result in better code, but there was no obvious difference in terms of decency (@fig-role-1) or consistency (@fig-role-2). Although it is notable that there are no responses rated 1/5 with the "Expert" role. Their mean decency did not differ by much in either case with 3.12 and 3.32 for "Helpful" and "Expert", respectively, while mean consistency was 3.35 and 3.19.

@@

The responses that "excelled" in their decency scores tended to bring a new tool beyond what was in the gold standard code suite -- for instance, generating a class with functions, or saving the results as a JSON.
